Effects of Water Permeability on the Hydrodynamics of a Vesicle Under Flow and Confinement

### 2020-12-29 vesicle_code/docs/permeableVes/main.tex
first draft of supplementary material

@@

\section*{Supplementary Material}
\subsection*{Formulation}
We consider a two-dimensional inextensible semi-permeable vesicle,
$\gamma$, suspended in unconfined and confined geometries. The
suspending fluid is assumed to be viscous so that the fluid velocity
$\uu$ and pressure $p$ are governed by the incompressible Stokes
equations
\begin{align}
  \label{eqn:governing}
  -\nabla p + \mu \triangle \uu = 0, \quad
  \nabla \cdot \uu = 0, \qquad \xx \in \RR^2 \setminus \gamma,
\end{align}
where $\mu$ is the fluid viscosity. In an unconfined geometry, the
condition $\uu(\xx) \rightarrow \uu_\infty(\xx)$ is enforced as $\xx
\rightarrow \infty$, and in a confined geometry with boundary $\Gamma$,
the boundary condition $\uu(\xx) = \UU(\xx)$ is enforced on $\Gamma$,
where $\UU(\xx)$ is prescribed. Along the vesicle $\gamma$, mass
continuity, a force balance, and local inextensibility are enforced by
requiring
\begin{align}
  \label{eqn:jump}
  \jump{\uu} = 0, \quad
  \jump{T\cdot\nn} = \ff_\mathrm{mem}, \quad
  \xx_s \cdot \uu_s = 0,
\end{align}
where $\nn$ is the outward normal of $\gamma$, $\jump{\cdot}$ is the
jump across the interface, and $T$ is the hydrodynamic stress tensor.
The membrane force $\ff_\mathrm{mem}$ is the sum of a bending force
with bending modulus $k_b$ and a force due to the tension $\Lambda$.
Following~\cite{vee-gue-zor-bir2009}, we modify the bending and tension
forces as $\ff_\mathrm{ben} = -k_b \xx_{ssss}$, and $\ff_\mathrm{ten} =
(\sigma \xx_s)_s$, where $s$ is arclength. The physical tension can be
recovered using the identity $\Lambda = \sigma + 1.5 \kappa^2$, where
$\kappa$ is the membrane curvature.

Semi-permeability is introduced by modifying the vesicle velocity from
the standard choice. Instead of using the no-slip boundary condition, we
assume the fluid flux through the boundary is proportional to the
mechanical force~\cite{yao-mor2017}. That is, 
\begin{align}
  \label{eqn:vesicleFlux}
  \uu - \dot{\xx} = - k_w (\ff_\mathrm{mem} \cdot \nn) \nn, \qquad
  \xx \in \gamma,
\end{align}
where $k_w$ is the water permeability.

The governing equations are non-dimensionalized by introducing a length
scale that we take to be $R_0 = 10^{-6}$m. Using a bending stiffness of
$k_b = 10^{-19}$J and fluid viscosity $5 \times 10^{-2}$kg/ms, we define
the time scale $\tau = \mu R_0^3/k_b = 0.5s$, the velocity scale $U =
R_0/\tau = 2\mu$m/s, the pressure scale $P = k_b/R_0^3 = 10^{-1}$Pa, the
tension scale $Q = k_b/R_0 = 10^{-13}$N, and the permeability scale $W =
R_0\mu = 2 \times 10^{-5}$m$^2$s/kg. The other standard dimensionless
variable of a vesicle is its reduced area $\nu = 4\pi A/L^2 \in (0,1]$.
The length $L$ is conserved by the local inextensibility condition.
However, the area $A$ is not conserved because of semi-permeability, and
therefore $\nu$ is also not conserved.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Integral equation formulation}
Since the fluid satisfies the Stokes equations, it can be represented as
layer potential. Given the interfacial boundary
conditions~\eqref{eqn:jump}, the fluid velocity is
\begin{align}
  \uu(\xx) = \uu_\infty(\xx) + \SS[\ff_\mathrm{mem}](\xx), \quad
    \xx \in \Omega,
\end{align}
where $\SS$ is the single-layer potential
\begin{align}
  \SS[\ff](\xx) = \frac{1}{4\pi\mu} \int_{\gamma} \left(
    -\mathbf{I} \log\rho + \frac{\rr \otimes \rr}{\rho^2} \right)
    \ff(\yy) ds_{\yy},
\end{align}
with $\rr = \xx - \yy$ and $\rho = \norm{\rr}$. Imposing the flux
condition~\eqref{eqn:vesicleFlux} and the inextensibility condition, the
vesicle velocity satisfies
\begin{align}
  \label{eqn:vesVelocity}
  \dot{\xx} &= \uu_\infty(\xx) + \beta (\ff_\mathrm{mem}\cdot\nn)\nn
  + \SS [\ff_\mathrm{mem}](\xx),  \quad
  \xx_s \cdot \dot{\xx}_s = 0.
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection*{Dimensionless equations}
%The inextensibility condition guarantees that the vesicle's length, $L$,
%is conserved, while its area, $A$, can change due to semi-permeability.
%Therefore, the reduced area $\alpha = 4\pi A/L^2 \in (0,1]$ is not
%conserved. We non-dimensionalize~\eqref{eqn:vesVelocity} by introducing
%the length scale $R_0 = L/2\pi$ and defining the time scale $\tau = \mu
%R_0^3/k_b$, the tension scale $Q = k_b/R_0^2$, and the permeability
%scale $W = R_0/\mu$. The background velocity $\uu_\infty$ is
%non-dimensionalized with $R_0/\tau$.
%
%In each experiment, we initialize an elliptical vesicle with longest
%diameter of 9$\mu$m. We use a length scale of $R_0 = 10^{-6}$m, a
%bending stiffness of $k_b = 10^{-19}$J, and fluid viscosity of $\mu=5
%\times 10^{-2}$kg/ms. Using the relaxation time scale $\tau = \mu
%R_0^3/k_b = 5 \times 10^{-1}$s, the pressure scale is $P = k_b/R_0^3 =
%10^{-1}$Pa.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Area dynamics}
Following the analysis of Veerapaneni et al.~\cite{vee-raj-bir-pur2009},
we compute the steady state shape of a semi-permeable vesicle in a
quiescent flow. The steady state shape is a stationary point of the
Lagrangian
\begin{align}
  \mathcal{L} = \frac{1}{2}\int_{\gamma} \kappa^2 \, ds +
    \Lambda \left(\int_{\gamma} ds  - L \right),
\end{align}
where the Lagrange multiplier $\Lambda$ is the tension. Note the absence
of the pressure Lagrange multiplier since the vesicle's area fluctuates.
Taking the variation of $\mathcal{L}$ with respect to $\gamma$ and
setting it to zero, the steady state shape satisfies $\kappa_{ss} +
\frac{1}{2}\kappa^3 - \Lambda \kappa = 0$, with initial conditions
$\kappa(0) = \kappa_0$ and $\kappa_s(0) = 0$.  Integrating once, we have
\begin{align}
  \frac{\kappa_s^2}{2} + \frac{\kappa^4}{8} - 
    \frac{\Lambda}{2}\kappa^2 = \frac{\kappa_0^4}{8} - 
    \frac{\Lambda}{2}\kappa_0^2.
  \label{eqn:curveODE}
\end{align}
Assuming $\kappa_s \neq 0$,~\eqref{eqn:curveODE} is separable, and can
be solved analytically in terms of the {\em EllipticF} function using
Mathematica. Unlike in the impermeable case~\cite{vee-raj-bir-pur2009},
the solution of~\eqref{eqn:curveODE} is not periodic unless $\kappa(s) =
\kappa_0$. Therefore, the steady state shape of a semi-permeable vesicle
in a quiescent flow is a circle with radius $L/2\pi$. Therefore, the
steady state curvature and tension are
\begin{align}
  \kappa = \frac{2\pi}{L}, \: \Lambda = \frac{2\pi^2}{L^2}.
  \label{eqn:SSshape}
\end{align}
Note that in contrast to a impermeable vesicle, the tension is positive
rather than negative.

We also compute the transient area of the vesicle. Since the area of the
vesicle is
\begin{align}
  A(t) = \frac{1}{2}\int_{\gamma} (\xx \cdot \nn)\, ds,
  \label{eqn:area}
\end{align}
its derivative includes terms due to the time derivative of $\xx \cdot
\nn$ and a term due to interface stretching~\cite{lai-tse-hua2008}, but
this latter term term is zero because of the local inextensibility
condition. Therefore,
\begin{align}
  \dot{A}(t) =
  \frac{1}{2} \int_{\gamma} (\dot{\xx} \cdot \nn)\, ds  + 
  \frac{1}{2} \int_{\gamma} (\xx \cdot \dot{\nn})\, ds.
\end{align}
Applying integration by parts, the two integrals agree, and we have
%\begin{align}
%  \int_\gamma (\xx \cdot \dot{\nn})\, ds 
%    = \int_\gamma \left(\xx \cdot \dot{\xx}_s^\perp \right)
%    = -\int_\gamma \left(\xx^\perp \cdot \dot{\xx}_s\right)\, ds 
%    = \int_\gamma \left(\xx_s^\perp \cdot \dot{\xx}\right)\, ds 
%    = \int_\gamma (\dot{\xx} \cdot \nn)\, ds.
%\end{align}
\begin{align}
  \dot{A}(t) = \int_\gamma \left(\beta (\ff \cdot \nn)\nn 
    + \SS[\ff]\right) \cdot \nn\, ds 
  = \beta \int_\gamma (\ff \cdot \nn)\, ds,
\end{align}
where we have used the incompressibility of the single-layer potential.
Repeatedly applying integration by parts, we have
\begin{align}
  \dot{A}(t) &= \beta \int_\gamma \left( -\xx_{ssss} + 
    (\sigma \xx_s)_s \right) \cdot \nn \, ds \\
  &= -\beta \int_\gamma \left(-\xx_{sss} + \sigma \xx_s 
    \right) \cdot \kappa \xx_s \, ds \\
  &= -\beta \int_\gamma \left(\xx_{ss} \cdot 
    (\kappa \xx_s)_s + \kappa \sigma \right) \, ds \\
  &= -\beta \int_\gamma \left(\kappa (\xx_{ss} \cdot \xx_{ss}) + 
    \kappa_s (\xx_{ss} \cdot \xx_s) + \kappa \sigma \right) 
    \, ds \\
  &= -\beta \int_\gamma \left(\kappa^3 + \kappa \sigma \right) 
    \, ds = \beta \int_\gamma \left(
    \frac{\kappa^3}{2} - \kappa \Lambda \right) \, ds.
  \label{eqn:areaROC}
\end{align}
Note that~\eqref{eqn:SSshape} and are consistent since the constant
curvature and tension values cause the integrand to vanish.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Supplementary Material: Numerical Methods}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Discretization in Space}
By using a boundary integral equation formulation, the unknowns are the
vesicle's position and tension that we track at $N$ discretization
points. Derivatives are computed with Fourier differentiation, and the
eighth-order quadrature~\cite{alp1999} is applied to the single-layer
potential. For constricted flows, nearly-singular integrals are computed
with an interpolation-based quadrature rule~\cite{qua-bir2014}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Discretization in Time}
To eliminate stringent time step restrictions, we modify a time stepping
method that discretizes high-order derivatives
semi-implicitly~\cite{vee-gue-zor-bir2009}. We introduce the notation
\begin{alignat}{3}
  &B[\xx]\ff = -\frac{d^4}{ds^4} \ff,  \qquad
  &&T[\xx]\sigma = (\sigma \xx_s)_s, \\
  &D[\xx]\ff = \xx_s \cdot \ff_s, 
  &&P[\xx]\ff = (\ff \cdot \nn) \nn,
\end{alignat}
for the differential and projection operators. Letting $B^N$ be the
bending operator due to the vesicle configuration at time $t^N$, and
similar notation for the other operators, we use the first-order
semi-implicit time stepping method
\begin{alignat}{3}  
  \frac{\xx^{N+1} - \xx^N}{\Delta t} &= \uu_\infty(\xx^N) 
  &&+ \beta P^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right) \nonumber \\
  & &&+ \SS^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right), 
\end{alignat}
and  the inextensibility condition is discretized as
\begin{align}
  D^N\xx^{N+1} &= 1.
\end{align}
To achieve second-order accuracy over long time horizons, we modify an
adaptive spectral deferred correction time stepping
method~\cite{qua-bir2016}. Since the area of the vesicle is not
conserved, we only use the length of the vesicle to estimate the error
which determines if a time step is accepted or not and determines the
subsequent time step size.

\subsection*{Numerical validation: An impermeable vesicle in a Poiseuille flow}
To validate our methods,
in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
for the steady state shape of an impermeable vesicle
vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
qualitatively agree, Kaoui et al.~report that the vesicles with
$\alpha=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
axisymmetric. In our simulations these vesicles are slightly asymmetric,
are undergoing a tank treading motion, and we therefore report them as
asymmetric slippers.

>>>>

\section*{Supplementary Material: Formulation}
We consider a two-dimensional inextensible semi-permeable vesicle,
$\gamma$, suspended in unconfined and confined geometries $\Omega$. The
suspending fluid is assumed to be viscous so that the fluid velocity
$\uu$ and pressure $p$ are governed by the incompressible Stokes
equations
\begin{align}
  \label{eqn:governing}
  -\nabla p + \mu \triangle \uu = 0, \quad
  \nabla \cdot \uu = 0, \qquad \xx \in \Omega \setminus \gamma,
\end{align}
where $\mu$ is the fluid viscosity. In an unconfined geometry, the
condition $\uu(\xx) \rightarrow \uu_\infty(\xx)$ is enforced as $\xx
\rightarrow \infty$, and in a confined geometry, the boundary condition
$\uu(\xx) = \UU(\xx)$ is enforced on $\partial \Omega$, where $\UU(\xx)$
is prescribed. Along the vesicle $\gamma$, mass continuity, a force
balance, and local inextensibility are enforced by requiring
\begin{align}
  \label{eqn:jump}
  \jump{\uu} = 0, \quad
  \jump{T\cdot\nn} = \ff_\mathrm{mem}, \quad
  \xx_s \cdot \uu_s = 0,
\end{align}
where $\nn$ is the outward normal of $\gamma$, $\jump{\cdot}$ is the
jump across the interface, and $T$ is the hydrodynamic stress tensor.
The membrane force $\ff_\mathrm{mem}$ is the sum of a bending force
with bending modulus $k_b$ and a force due to the tension $\Lambda$.
Following~\cite{vee-gue-zor-bir2009}, we modify the bending and tension
forces as $\ff_\mathrm{ben} = -k_b \xx_{ssss}$, and $\ff_\mathrm{ten} =
(\sigma \xx_s)_s$, where $s$ is arclength. The physical tension can be
recovered using the identity $\Lambda = \sigma + 1.5 \kappa^2$, where
$\kappa$ is the membrane curvature.

Semi-permeability is introduced by modifying the vesicle velocity from
the standard no-slip condition $\cdot{\xx} = \uu(\xx)$, where $\xx(s,t)$
parameterizes the vesicle shape $\gamma$ at time $t$ with respect to
arclength. Instead, we consider the case where the flux through the
vesicle is proportional to the mechanical force~\cite{yao-mor2017}. That
is, 
\begin{align}
  \label{eqn:vesicleFlux}
  \uu - \dot{\xx} = - k_w (\ff_\mathrm{mem} \cdot \nn) \nn, \qquad
  \xx \in \gamma,
\end{align}
where $k_w$ is the water permeability.

The governing equations are non-dimensionalized by introducing a length
scale that we take to be $R_0 = 10^{-6}$m. Using a bending stiffness of
$k_b = 10^{-19}$J and fluid viscosity $5 \times 10^{-2}$kg/ms, we define
the time scale $\tau = \mu R_0^3/k_b = 0.5s$, the velocity scale $U =
R_0/\tau = 2\mu$m/s, the pressure scale $P = k_b/R_0^3 = 10^{-1}$Pa, the
tension scale $Q = k_b/R_0 = 10^{-13}$N, and the permeability scale $W =
R_0\mu = 2 \times 10^{-5}$m$^2$s/kg. Another standard dimensionless
variable in vesicle suspensions is the reduced area $\nu = 4\pi A/L^2
\in (0,1]$, where $L$ is the vesicle length and $A$ is its area. The
length is conserved by the local inextensibility condition, but the area
is not because of semi-permeability. Therefore, the reduced area is
dynamic.

Since the fluid satisfies the Stokes equations, its velocity can be
represented as a layer potential. Given the interfacial boundary
conditions~\eqref{eqn:jump}, the fluid velocity is
\begin{align}
  \uu(\xx) = \uu_\infty(\xx) + \SS[\ff_\mathrm{mem}](\xx), \quad
    \xx \in \Omega,
\end{align}
where $\SS$ is the single-layer potential
\begin{align}
  \SS[\ff](\xx) = \frac{1}{4\pi\mu} \int_{\gamma} \left(
    -\mathbf{I} \log\rho + \frac{\rr \otimes \rr}{\rho^2} \right)
    \ff(\yy) ds_{\yy},
\end{align}
with $\rr = \xx - \yy$ and $\rho = \norm{\rr}$. Imposing the flux
condition~\eqref{eqn:vesicleFlux} and the inextensibility condition, the
vesicle velocity satisfies the boundary integral equation
\begin{align}
  \label{eqn:vesVelocity}
  \dot{\xx} &= \uu_\infty(\xx) + \beta (\ff_\mathrm{mem}\cdot\nn)\nn
  + \SS [\ff_\mathrm{mem}](\xx),  \quad
  \xx_s \cdot \dot{\xx}_s = 0,
\end{align}
where $\beta = k_w/W$ is the dimensionless water permeability. In
confined geometries, the far field term $\uu_\infty$ is replaced by a
double-layer potential with a density defined on $\partial\Omega$. The
unknown density function allows us to satisfy the Dirichlet boundary
condition $\uu(\xx) = \UU(\xx)$ for $\xx \in \partial\Omega$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Supplementary Material: Vesicle Area}
In the absence of an imposed flow, the steady state vesicle shape and a
differential equation for the area of the vesicle can be derived. We
start by following the analysis of Veerapaneni et
al.~\cite{vee-raj-bir-pur2009} by computing the steady state shape of a
semi-permeable vesicle in a quiescent flow. The steady state shape is a
stationary point of the Lagrangian
\begin{align}
  \mathcal{L} = \frac{1}{2}\int_{\gamma} \kappa^2 \, ds +
    \Lambda \left(\int_{\gamma} ds  - L \right),
\end{align}
where the Lagrange multiplier $\Lambda$ is the tension. Note the absence
of the pressure Lagrange multiplier since the vesicle's area fluctuates.
Taking the variation of $\mathcal{L}$ with respect to $\gamma$ and
setting it to zero, the steady state shape satisfies $\kappa_{ss} +
\frac{1}{2}\kappa^3 - \Lambda \kappa = 0$, with initial conditions
$\kappa(0) = \kappa_0$ and $\kappa_s(0) = 0$.  Integrating once, we have
\begin{align}
  \frac{\kappa_s^2}{2} + \frac{\kappa^4}{8} - 
    \frac{\Lambda}{2}\kappa^2 = \frac{\kappa_0^4}{8} - 
    \frac{\Lambda}{2}\kappa_0^2.
  \label{eqn:curveODE}
\end{align}
Assuming $\kappa_s \neq 0$,~\eqref{eqn:curveODE} is separable, and can
be solved analytically in terms of the {\em EllipticF} function using
Mathematica. Unlike in the impermeable case, the solution
of~\eqref{eqn:curveODE} is not periodic unless $\kappa(s) = \kappa_0$.
Therefore, the steady state shape of a semi-permeable vesicle in a
quiescent flow is a circle with radius $L/2\pi$. Therefore, the steady
state curvature and tension are $\Lambda = 2\pi^2/L^2.$ Note that in
contrast to a impermeable vesicle, the tension is positive rather than
negative.

We next compute the transient area of the vesicle. Since the area of the
vesicle is
\begin{align}
  A(t) = \frac{1}{2}\int_{\gamma} (\xx \cdot \nn)\, ds,
  \label{eqn:area}
\end{align}
its derivative includes terms due to the time derivative of $\xx \cdot
\nn$ and a term due to interface stretching~\cite{lai-tse-hua2008}, but
this latter term term is zero because of the local inextensibility
condition. Therefore,
\begin{align}
  \dot{A}(t) =
  \frac{1}{2} \int_{\gamma} (\dot{\xx} \cdot \nn)\, ds  + 
  \frac{1}{2} \int_{\gamma} (\xx \cdot \dot{\nn})\, ds.
\end{align}
Applying integration by parts, the two integrals agree, and we have
%\begin{align}
%  \int_\gamma (\xx \cdot \dot{\nn})\, ds 
%    = \int_\gamma \left(\xx \cdot \dot{\xx}_s^\perp \right)
%    = -\int_\gamma \left(\xx^\perp \cdot \dot{\xx}_s\right)\, ds 
%    = \int_\gamma \left(\xx_s^\perp \cdot \dot{\xx}\right)\, ds 
%    = \int_\gamma (\dot{\xx} \cdot \nn)\, ds.
%\end{align}
\begin{align}
  \dot{A}(t) = \int_\gamma \left(\beta (\ff \cdot \nn)\nn 
    + \SS[\ff]\right) \cdot \nn\, ds 
  = \beta \int_\gamma (\ff \cdot \nn)\, ds,
\end{align}
where we have used the incompressibility of the single-layer potential.
Repeatedly applying integration by parts, we have
\begin{align}
  \dot{A}(t) &= \beta \int_\gamma \left( -\xx_{ssss} + 
    (\sigma \xx_s)_s \right) \cdot \nn \, ds \\
  &= -\beta \int_\gamma \left(-\xx_{sss} + \sigma \xx_s 
    \right) \cdot \kappa \xx_s \, ds \\
  &= -\beta \int_\gamma \left(\xx_{ss} \cdot 
    (\kappa \xx_s)_s + \kappa \sigma \right) \, ds \\
  &= -\beta \int_\gamma \left(\kappa (\xx_{ss} \cdot \xx_{ss}) + 
    \kappa_s (\xx_{ss} \cdot \xx_s) + \kappa \sigma \right) 
    \, ds \\
  &= -\beta \int_\gamma \left(\kappa^3 + \kappa \sigma \right) 
    \, ds = \beta \int_\gamma \left(
    \frac{\kappa^3}{2} - \kappa \Lambda \right) \, ds.
  \label{eqn:areaROC}
\end{align}
Note that the integrand in~\eqref{eqn:areaROC} is zero when the vesicle
reaches its steady state which guarantees that $\dot{A}(t) = 0$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Supplementary Material: Numerical Methods}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Discretization in Space}
By using a boundary integral equation formulation, the unknowns are the
vesicle's position and tension that we track at $N$ collocation points.
Derivatives are computed with Fourier differentiation, and the
eighth-order quadrature~\cite{alp1999} is applied to the single-layer
potential. For confined geometries, the trapezoid rule is used to
approximate the double-layer potential since its kernel is smooth and
periodic. Nearly-singular integrals are computed with an
interpolation-based quadrature rule~\cite{qua-bir2014}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Discretization in Time}
To eliminate stringent time step restrictions, we modify a time stepping
method that discretizes high-order derivatives
semi-implicitly~\cite{vee-gue-zor-bir2009}. We introduce the notation
\begin{alignat}{3}
  &B[\xx]\ff = -\frac{d^4}{ds^4} \ff,  \qquad
  &&T[\xx]\sigma = (\sigma \xx_s)_s, \\
  &D[\xx]\ff = \xx_s \cdot \ff_s, 
  &&P[\xx]\ff = (\ff \cdot \nn) \nn,
\end{alignat}
for the differential and projection operators. Then, the
governing equations~\eqref{eqn:vesVelocity} are
\begin{align}
  \dot{\xx} &= \uu_\infty(\xx) + \beta P(B\xx + T\sigma)
  + \SS (B\xx + T\sigma), \quad
  D \dot{\xx} = 0, 
\end{align}
We note that the integral and differential operators, which all depend
on the vesicle shape, are non-linear with respect to the vesicle
shape. We construct a time stepping scheme by letting $B^N$ be the
bending operator due to the vesicle configuration at time $t^N$, and use
similar notation for the other operators. Then, a first-order
semi-implicit time stepping method of~\eqref{eqn:vesVelocity} is
\begin{alignat}{3}  
  \frac{\xx^{N+1} - \xx^N}{\Delta t} &= \uu_\infty(\xx^N) 
  &&+ \beta P^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right) \nonumber \\
  & &&+ \SS^N\left(B^N\xx^{N+1} + T^N\sigma^{N+1}\right),  \\
  D^N\xx^{N+1} &= 1.
\end{alignat}
This is a linear system that we solve with matrix-free GMRES.

To achieve second-order accuracy over long time horizons, we modify an
adaptive spectral deferred correction time stepping
method~\cite{qua-bir2016}. Since the area of the vesicle is not
conserved, we only use the length of the vesicle to estimate the error
which determines if a time step is accepted or not and determines the
subsequent time step size.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Numerical Validation}
To validate our methods, we construct a phase diagram of the steady
state shape of an impermeable vesicle in a Poiseuille flow. Depending on
the flow rate and the reduced area, the steady state vesicle becomes
either a symmetric bullet or parachute, or an asymmetric
slipper~\cite{kao-bir-mis2009}. Comparing our results
(Figure~\ref{fig:PoiseuillePhase}) with those in~\cite{kao-bir-mis2009}
(see Figure 2), we see that the results qualitatively agree. We note
that Kaoui et al.~report that the vesicles with $\alpha=0.7$ and flow
rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are axisymmetric. In our
simulations these vesicles are slightly asymmetric, are undergoing a
tank treading motion, and we therefore report them as asymmetric
slippers.
\begin{figure}[htp]
  \centering
  \ifTikz
  \input{figures/parabolicImpermeable.tikz}
  \else
  \includegraphics{figures/parabolicImpermeable.pdf}
  \fi
  \caption{\label{fig:PoiseuillePhase} Phase diagram of an impermeable
  vesicle with various flow rates and reduced areas. The shapes agree
  qualitatively with Kaoui et al.~\cite{kao-bir-mis2009} (see Figure
  2).}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection*{Dimensionless equations}
%The inextensibility condition guarantees that the vesicle's length, $L$,
%is conserved, while its area, $A$, can change due to semi-permeability.
%Therefore, the reduced area $\alpha = 4\pi A/L^2 \in (0,1]$ is not
%conserved. We non-dimensionalize~\eqref{eqn:vesVelocity} by introducing
%the length scale $R_0 = L/2\pi$ and defining the time scale $\tau = \mu
%R_0^3/k_b$, the tension scale $Q = k_b/R_0^2$, and the permeability
%scale $W = R_0/\mu$. The background velocity $\uu_\infty$ is
%non-dimensionalized with $R_0/\tau$.
%In each experiment, we initialize an elliptical vesicle with longest
%diameter of 9$\mu$m. We use a length scale of $R_0 = 10^{-6}$m, a
%bending stiffness of $k_b = 10^{-19}$J, and fluid viscosity of $\mu=5
%\times 10^{-2}$kg/ms. Using the relaxation time scale $\tau = \mu
%R_0^3/k_b = 5 \times 10^{-1}$s, the pressure scale is $P = k_b/R_0^3 =
%10^{-1}$Pa. 

@@
